Generalized Universe Hierarchies and First-Class Universe Levels

### 2021-07-12 paper.tex
new sub minor fixes

We provide an Agda formalization of the contents of the paper. The formalization
is not complete, as we skip proofs involving an excessive number of equality
coercions (which are more suited to informal reasoning, using equality
reflection), and instead focus on the key points.

@@

There are other ways for presenting the basic categorical structure of models,
which are nonetheless equivalent to cwfs, including natural models
\cite{awodey18natural} and categories with attributes \cite{cartmellthesis}. We
use the cwf presentation for its immediately algebraic character and closeness
to conventional explicit substitution syntax.

@@

Second, could we use weaker type-theoretic features, like super universes
\cite{Palmgren98onuniverses} or Mahlo universes \cite{setzer00mahlo}? These are
sufficient to model transfinite hierarchies. However, it is not clear how to
additionally support \emph{recursive sub-universes}, which in our work corresponds to
the type former preservation property of $\Lift$. Thus, we give a custom IR
definition which corresponds more directly to TTGU structure.

>>>>

We provide an Agda formalization of the contents of the paper at
\url{https://github.com/AndrasKovacs/universes/tree/master/agda}. The
formalization is not complete, as we skip proofs involving an excessive number
of equality coercions (which are more suited to informal reasoning, using
equality reflection), and instead focus on the key points.

@@

There are other ways for presenting the basic categorical structure of models,
which are nonetheless equivalent to cwfs, including natural models
\cite{awodey18natural} and categories with attributes \cite{cartmellthesis}. We
use the cwf presentation for its immediately algebraic character and closeness
to conventional explicit substitutions. We consider the syntax of a type theory
to be its initial model.

@@

Second, could we use simpler type-theoretic features, like super universes
\cite{Palmgren98onuniverses} or Mahlo universes \cite{setzer00mahlo}? These are
sufficient to model transfinite hierarchies. However, it is not clear how to
additionally support \emph{recursive sub-universes}, which in our work corresponds to
the type former preservation property of $\Lift$. Thus, we give a custom IR
definition which corresponds more directly to TTGU structure.
